Dissertation

### 2024-04-15 Manuscript/pre_sections/pre_html.qmd
big re-render of all versions

<div style="text-align: center; margin-top: 50px; font-size: 24px; font-weight: bold;">
  The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach
</div>

@@

<!-- Second Page and so on... -->
<div style="text-align: justify; margin-top: 700px;">
  Submitted to the faculty of the University Graduate School in partial fulfillment of the
  requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
  Sciences and the Cognitive Science Program, Indiana University
  Indiana University
</div>

<div style="margin-top: 400px;">
  <!-- Your page numbering if needed -->
</div>

<div style="page-break-before: always;"></div>

<!-- Committee Members Page -->
<div style="text-align: center; margin-top: 300px;">
  Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
  requirements for the degree of Doctor of Philosophy.
</div>

<div style="text-align: center; margin-top: 300px;">
  _____________________________  Robert L. Goldstone<br><br>
  _____________________________  Robert Nosofsky<br><br>
  _____________________________  Peter Todd<br><br>
  _____________________________  Mike Jones
</div>

<div style="page-break-before: always;"></div>

<div style="page-break-before: always;"></div>

<!-- Acknowledgements -->
<div style="text-align: center; font-weight: bold; font-size: 24px;">
  Acknowledgements
</div>
<div style="text-align: center; margin-top: 700px; font-size: 24px;">

</div>

<div style="page-break-before: always;"></div>

>>>>

<div style="text-align: center; margin-top: 50px; font-size: 24px; font-weight: bold;">
 The Role of Variability in Learning Generalization: A Computational Modeling Approach
</div>

@@

### 2024-04-15 Manuscript/pre_sections/pre_pdf.qmd
manuscript update
fix docx and html. Update htw with embed
add supplementals
adjust appendices
render full in pdf and markdown
big re-render of all versions

\begin{centering}
\LARGE
{Variability and Generalization - A Similarity-Based Account}

@@

\vspace{11.5cm}

@@

Submitted to the faculty of the University Graduate School in partial fulfillment of the
requirements for the degree Doctor of Philosophy in the Department of Psychology and Brain
Sciences and the Cognitive Science Program, Indiana University
Indiana University

@@

Accepted by the Graduate Faculty, Indiana University, in partial fulfillment of the
requirements for the degree of Doctor of Philosophy.
\vspace{4cm}

\
\_____________________________  Robert L. Goldstone
\vspace{2.5cm}
\
\
\_____________________________  Robert Nosofsky
\vspace{2.5cm}
\
\_____________________________  Peter Todd
\vspace{2.5cm}
\
\_____________________________  Mike Jones

\begin{centering}

\vspace*{6.5cm}

@2023 \\
\vspace{1cm}

Thomas E. Gorman
\vspace{.2cm}

\vspace{5cm}

\newpage
\begin{center}
\textbf{Acknowledgements}
\end{center}
\newpage

\tableofcontents
\newpage
\listoffigures
\newpage
\listoftables
\newpage

>>>>

\begin{centering}
\LARGE
{The Role of Variability in Learning Generalization: A Computational Modeling Approach}

@@

\vspace{16.5cm}

@@

@@
